{\sc Kalashnikov}: Fully Automatic Loop Free Program Synthesis by Bounded Model Checking

### 2013-10-04 paper/paper.tex
nudges to abstract

\begin{abstract}
We present a method for synthesizing loop-free programs, using a combination of
bounded model checking and explicit state model checking.  The user provides a
specification in plain C, after which the synthesis process is fully automatic.

>>>>

\begin{abstract}
We present a simple-yet-effective method for synthesizing loop-free
programs, using a novel combination of Bounded Model Checking and
explicit-state Model Checking.  The user provides a specification in plain
C, after which the synthesis process is fully automatic.
